---
title: "Demonstration of risk-of-bias visualisation tools in Rmarkdown"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(robvis)
library(knitr)
library(kableExtra)
library(plyr)
data <- data_rob2
tool <- "ROB2"
colour <- "cochrane"
# colour <- "colourblind"
```

## 1. Risk-of-bias written summary
`r nrow(data) ` studies were assessed for risk of bias using the ROB2.0 assessment tool. Of those, `r nrow(data[ which(data$Overall == "Low"),]) ` studies were at overall "Low risk of bias", `r nrow(data[ which(data$Overall == "High"),]) ` were at "High risk of bias", and authors had "Some concerns" for `r nrow(data[ which(data$Overall == "Some concerns"),]) ` studies.

## 2. Risk-of-bias table
```{r cars, echo=FALSE}
kable(data,
          booktabs = TRUE) %>%
          kable_styling(latex_options = "scale_down")
```

## 3. Figures
### 3.1 Weighted summary bar plot
```{r barplot, echo=FALSE, fig.width = 8, align = "left"}
rob_summary(data, tool, overall = TRUE, weighted = TRUE, colour = colour)
```

### 3.2 Traffic-light plot
```{r trafficlight, echo=FALSE, fig.height = 10}
rob_traffic_light(data, tool, colour = colour)
```
